[Artifact57] Robust Resource Bounds with\\ Static Analysis and Bayesian Inference

### 2024-03-09 README/step_by_step_instructions.tex
typo

In this section, we demonstrate how to produce tables and plots in the paper
from the experiment results that are stored in each benchmark's \texttt{bin}
directory.
%
In the Docker container, the \texttt{bin} directory of each benchmark already
contains the experiment results that we reported in the paper.
%
We will demonstrate how to generate the experiment results from scratch in
\cref{sec:generate experiment results}.

>>>>

In this section, we demonstrate how to produce tables and plots in the paper
from the experiment results that are stored in each benchmark's \texttt{bin}
directory.
%
In the Docker container, the \texttt{bin} directory of each benchmark already
contains the experimental results that we reported in the paper.
%
We will demonstrate how to generate the experimental results from scratch in
\cref{sec:generate experiment results}.
